\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-30 Report/project_report.tex
Updated plots for new noise params and changed aspect ratios

>>>>

\begin{figure}
    \centering
    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/RMSE-Comparison-Feat-Density-1215-1715-Trans}
        \label{fig:comp_3:trans_err}
    }

    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/RMSE-Comparison-Feat-Density-1215-1715-Rot}
        \label{fig:comp_3:rot_err}
    }

    \caption{Comparison of cumulative Root Mean Squared Error (RMSE) of MSCKF, SWF, and IMU integration for three different synthetic maps generated based on the IMU data in the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' and ``SWF'' refer to the number of features in the dataset (20, 40 or 60).}
    \label{fig:comp_3}
\end{figure}
